\section*{Acknowledgments}
%To be completed

It isn't possible to do your Ph.D. work on a 3000 person collaboration and not 
come into contact with at least someone now and then. So I guess I have some people to thank.
I owe a tremendous amount to those people who have believed in me,
supported me, and helped me every single step of the way. First and foremost, I must
thank my advisor, Professor John Butler, for taking me on as a student before I had even stepped
foot in the classroom. Without your confidence in me and your steady hand
this could not have happened. I would also like to thank Professor Kevin Black
for being like a second advisor and a vital resource, even though
I left you stranded at the airport in Geneva that one time.
And I would be remiss to not also thank the other members of my committee, Professors Tulika
Bose, Ken Lane, and Shyam Erramilli, who have been very supportive
during my tenure as a student at Boston University. 


In my time working on ATLAS I have come in contact with many great and soon-to-be great 
physicists  who have shared their experience and expertise with me. Thank you for 
giving some of your time to me so that I could learn from you. 
Thank you to the faculty of the BU ATLAS group: John, Kevin, Steve, Jim, and Saul.
Special thanks to Saul for not losing it after the umpteenth time I crashed 
the tier 2 and tier 3 servers.
I must thank all of the BU ATLAS post-docs during my tenure, who are usually 
right there on the front lines with us poor graduate students: Rob, Zhen, Lidia, and Louis.
Louis, it is hard to overstate how essential you have been in developing what has become this thesis.
I am truly thankful for your wisdom, your persistence, and your friendship.
And last but certainly not least, I am thankful to all of the BU ATLAS graduate students 
who have been along with me for various stages of the ride: Jeremy, Mike, Clare, Alex, and Efe.


There are many important people in my life, without whom this whole experience would have been hopeless.
Kate and Caitlin, ``the Ckaitelyns'', this wouldn't have even gotten off the ground  if you both didn't have the guts to take this journey up to Boston with me.  And you're still stuck up here!  Sorry about that. You can always go back home, but I'd miss you if you did. 
Clare, I owe you so much for taking me under your wing. It's because of you that I had such a great experience in Geneva. Here's to many more good times in Boston!
Grant, thanks for putting up with me even though I made you feel old. I miss our debates over red wine and reindeer meat.
Bonnie, Grant, Michal, and Michelle, here's to Michal not driving off that cliff in Rapallo while dancing to Daft Punk on the radio. You made my time in Geneva too much fun.
Luke, thanks for traveling 3000 miles from home to the office across the street so that we could have lunch every day. Too bad we didn't have time to solve ALL of the world's problems!
John, all these years since I first set up my drums on Painted Tree Rd and we still don't have a band. It probably has something to do with this thing. Thanks for sticking with me anyway!
Ryan, thanks for keeping the spirit of North Carolina alive in Massachusetts. It's still pretty cold here, though, but maybe
if we wait long enough\dots~Jeff, we started the program on the same day and defended just one day apart! This makes me think of a song. \emph{Looks like we made it. Look how far we've come my baby. We mighta took the long way. We knew we'd get there someday. They said, ``I bet they'll never make it''. But just look at us holding on. We're still together still going strong.} Mmm\dots perhaps that was not the best choice.  Anyway, I still hate Garrison Keillor.
Chynna, you've helped me to realize that I should take a step back and appreciate more of what the world has to offer.
I may not have the same free spirit but I cherish yours. 
Katie, we've supported each other through our last years as students and I couldn't think of anyone better to share that
with. I'm looking forward to the next chapter in our lives together!
April, now that I'm a doctor I guess the lecturing is only gonna get worse. But you must be used to it by now, right?
Thank you for being such an amazing little sister.
Mom, Dad, Paul, Susan, how could I ever truly thank you? I know this at least, I would never have made it this far without knowing how much you believed in me every step of the way.  I love you all.
