% Resume 2.0 (2009-04-12)
% Copyright 2009 Zach Scrivena
% zachscrivena@gmail.com
% http://zs.freeshell.org/latexresume/
%
% This document is released under the
% Creative Commons Attribution 3.0 Unported License
% http://creativecommons.org/licenses/by/3.0/

%%%%%%%%%%%%%%
%% PREAMBLE %%
%%%%%%%%%%%%%%


\doublespacing

\setlength{\parindent}{0cm}
%\tabto{0.1\textwidth}

%%%%%%%%%%%%%%%%
%% NAME BLOCK %%
%%%%%%%%%%%%%%%%

\section*{Brian Alexander Long}


Year of Birth: 1988 \newline
Contact: \\
\cvtab{Department of Physics, Boston University}\\
\cvtab{Metcalf Science Center}\\
\cvtab{590 Commonwealth Ave}\\
\cvtab{Boston, MA 02215}\\
%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%



\section*{Education}

\href{http://buphy.bu.edu/}{Boston University}, Boston, Massachusetts \newline
\cvtab{Ph.D. Candidate in Physics, \datestamp{2010}{09}{10} -- Present}
%{\small Cumulative GPA of 3.78}

\href{http://www.buphy.bu.edu/}{Boston University}, Boston, Massachusetts \newline
\cvtab{M.A. in Physics, \datestamp{2015}{09}{25} }

\href{http://www.physics.unc.edu/}{The University of North Carolina}, Chapel Hill, North Carolina \newline
\cvtab{B.S. in Physics and Astronomy, \datestamp{2006}{09}{15} -- \datestamp{2010}{05}{15}}
%Cumulative GPA of 3.57}



%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Research Experience}

\href{http://www.atlas.ch}{{The ATLAS Experiment}, CERN, Meyrin, Switzerland} \newline
Graduate Research Fellow, High Energy Physics, Boston University, \datestamp{2010}{09}{} -- Present \newline
Advisor: Prof. John Butler
{\begin{itemize}
\item Conducting the first direct measurement of the W quartic gauge coupling while also searching for anomalous quartic gauge couplings in the \textit{WWW} production channel for the fully leptonic decay channel.
\item Performed search for exotic heavy charged gauge bosons in the leptonic decay channel using data collected from the Large Hadron Collider (LHC) in 2012 at a center-of-mass energy of 8~TeV. Significantly improves limits from previous searches within ATLAS.
\item Studied the performance of the ATLAS muon trigger system during 
the 2012 data collection run.  Demonstrated the robustness of the muon trigger system against pileup.
\item Performed timing studies of new fast muon trigger algortihm to 
be used in LHC Run 2.
\item Participated in upgrades and improvements to the ATLAS muon spectrometer system in preparation for LHC Run 2.  Resulted in finally 
bringing the ATLAS muon system to the full Technical Design Report specifications. Also helped in first complete test of the Muon Drift Tube (MDT) gas system.
\item Lead efforts to test custom ASD chips to be used in the MDT 
technology for future upgrades to the ATLAS muon system.
\end{itemize}
}

\href{http://www.tunl.duke.edu}{{Triangle Universities Nuclear Laboratory (TUNL)}, Duke University} \newline
Undergraduate Research Assistant, \datestamp{2008}{04}{15} -- \datestamp{2010}{05}{15} \newline
Advisor: Prof. Reyco Henning 
{\begin{itemize}
\item Built a muon veto system for a low background dark matter detector installed in the Kimballton Underground Reasearch Facility.
\item Performed Monte Carlo simulation of cosmogenically activated germanium in High-Purity Germanium detectors.
\item Developed software for use in low-background gamma spectroscopy analysis.
\end{itemize}
}

\href{http://www.cbp.lbl.gov/}{{Center for Beam Physics}, LBNL, Berkeley, California} \newline
Undergraduate Research Assistant, \datestamp{2009}{06}{15} -- \datestamp{2009}{08}{15} \newline
Advisor: Dr. Ji Qiang 
{\begin{itemize}
\item Developed software for the optimization of beam parameters
in the design of the photo-injector for the Next Generation Light Source (NGLS) project at LBNL.
\end{itemize}
}

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\section*{Publications}

%necessary to put a blank block in front of citation since first block
%doesn't do text wrapping
\begin{enumerate}
\parshape 2 0cm \linewidth \listindent \dimexpr\linewidth-\listindent\relax
\item[] The ATLAS Collaboration, ``Search for high-mass states with one lepton plus missing transverse momentum in \textit{pp} collisions 
at $\sqrt{s} = 8 $~TeV with the ATLAS detector``, Conference Result, \href{http://cds.cern.ch/record/1692660}{ATLAS-CONF-2014-017} (2014). To be submitted to JHEP.

\item[] The ATLAS Collaboration, ``Search for a \textit{WZ} resonance in the fully leptonic channel using \textit{pp} collisions at $\sqrt{s} = 8 $~TeV with the ATLAS detector``, Conference Result, \href{http://cds.cern.ch/record/1692369}{ATLAS-CONF-2014-015} (2014). To be submitted to Phys. Lett. B.

\item[] The ATLAS Collaboration, ``Performance of the ATLAS muon trigger in \textit{pp} collisions at $\sqrt{s} = 8$~TeV``, ATLAS-TRIG-2012-03 (2014). To be submitted to Eur. Phys. J. C.


\item[] \href{http://arxiv.org/abs/1007.0015}{Finnerty, P., Henning, R., Long, A., et al., ``Low-background gamma counting at the Kimballton Underground Research Facility``, \textit{Nuclear Instrumentation and Methods A}, Vol. 642 (2011) 65-69. }

\item[] Long, A., Qiang, J., ``Parallel Optimization of Beam Energy for a Next Generation Lighsource Photoinjector``, Abstract, \textit{DOE Journal of Undergraduate Research} (2009)

\end{enumerate}
%%%%%%%%%%%%%%%%%%
%% Conferences  %%
%%%%%%%%%%%%%%%%%%

\section*{Conference Experience~\& Citations}



\begin{enumerate}
\parshape 2 0cm \linewidth \listindent \dimexpr\linewidth-\listindent\relax

\item[] 2015 Open Data Science Conference, Boston, MA\newline
{Attended the first Open Data Science Conference, held in May of 2015 in Boston
}

\item[] 2015 American Physical Society April Meeting , Baltimore, MD\newline
{Presented talk on a "Search for $WWW\rightarrow l\nu l\nu l\nu$ production in the ATLAS detector at $\sqrt{s}=8$~TeV"
}

\item[] 2014 Fermilab-CERN Hadron Collider Physics Symposium, Batavia, IL\newline
{Attended as a student in a two week long summer school hosted at Fermilab intended to prepare graduate students and post-docs 
for pressing problems in collider physics.
}

\item[] 2009 American Physical Society April Meeting, Denver, Colorado \newline
{Finnerty, P., Henning, R., MacMullin, S., Macon, K., Long, A., Lindstrom, R.,
Back, H., Roundtree, S.D., "Commmisioning of a Gamma Counting Facility in the Kimballton
Mine"
} 

\item[] 2008 APS Division of Nuclear Physics Conference, Oakland, California \newline
{Poster through CEU program: Long, A., "Preparatory Low-Background Assay Analysis"
}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACADEMIC HONORS & AWARDS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Honors~\& Awards}


\begin{enumerate}
\parshape 2 0cm \linewidth \listindent \dimexpr\linewidth-\listindent\relax
\item[] Outstanding Teaching Fellow \hfill \datestamp{2010}{}{} -- \datestamp{2011}{}{} \newline
Boston University College of Arts and Sciences outstanding teaching fellow of the year in Physics.


\item[] DOE SULI Program Funding Award \hfill \datestamp{2009}{}{}\newline
{Full funding award for work with Center for Beam Physics at Lawrence-Berkeley National Lab.
}


\item[] APS CEU Full Travel Award \hfill \datestamp{2008}{}{} \newline
{2008 October Division of Nuclear Physics APS Meeting}

%Dean's list?

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Teaching Experience}

\begin{enumerate}
\parshape 2 0cm \linewidth \listindent \dimexpr\linewidth-\listindent\relax
\item[] Teaching Fellow, Department of Physics, Boston University \hfill \datestamp{2010}{09}{} -- \datestamp{2011}{05}{}\newline
{Teaching assisant for undergraduate physics courses.  Topics covered: Mechanics, Electromagnetism, Thermodynamics, Modern physics.}

\end{enumerate}



