\section{Background Estimates}
\label{sec:bg_estimates}

In \sec\ref{sec:www_bg_samples}, three categories of backgrounds
were listed based on the source
of final state leptons: prompt, photon, and fake
backgrounds. In this section, we will elaborate on how
each of these backgrounds are determined as well
as provide validation for each of these estimates using
control regions. Control regions are regions of phase space
that are selected to be enriched in a specific background
or collection of backgrounds while at the same time being
orthogonal to the signal regions of \sec\ref{sec:signal_regions},
or at least far enough removed so as not to bias the signal region
estimate.

The prompt and photon backgrounds are estimated using 
the MC simulation samples listed earlier in \sec\ref{sec:www_bg_samples}.
The most important of these backgrounds are the $WZ$, $ZZ$, 
and $Z\gamma$ backgrounds. The predictions for these backgrounds
are studied in \sec\ref{sec:mcbg}. Where appropriate, corrections
to the normalization
of these samples are applied to take into account higher order 
corrections; uncertainties on these corrections are also evaluated.

Even though the $WZ$ and $ZZ$ backgrounds predict
at least one SFOS pair from \z-boson decay,
they contaminate the 0 SFOS signal region,
explained in \sec\ref{sec:signal_regions}, in part because
of electron charge mis-identification.  The effect of 
electron charge mis-identification is evaluated in the data
and applied as a correction to the $WZ$ and $ZZ$ MC backgrounds
in the 0 SFOS region. This is covered in \sec\ref{sec:charge_misid}.

Finally, the fake backgrounds are determined 
using the data as a model. The details of the fake background
estimate and validation are presented in \sec\ref{sec:bg_fake}.





\subsection{Monte Carlo Backgrounds}
\label{sec:mcbg}
\input{www_estimate_mc}
\subsection{Electron Charge Mis-identification}
\label{sec:charge_misid}
\input{www_charge_misid}  
\subsection{Fake lepton background}
\label{sec:bg_fake}
\input{www_estimate_fake}
