\section{Data and Simulation Samples}
\subsection{Data}
\label{sec:subsection_data}


This analysis is based on the study of the full proton-proton collision
data from the LHC in 2012. The amount 
of data used in this analysis corresponds to 
an integrated luminosity of \lumi.
The uncertainty on the integrated luminosity is $1.9\%$ 
following the same methodology as in \cite{Aad:2013ucp}.
%from Van-der-Meer scans taken throughout 2012.
%read this citation.
The data are selected after requiring that at least one
of four single lepton triggers passed during data taking, 
specifically:
\begin{itemize}
\item[] Either at least one isolated electron with $\pt > 24 \GeV$
\item[] or at least one electron with $\pt > 60 \GeV$
\item[] or at least one isolated muon with $\pt > 24 \GeV$
\item[] or at least one muon with $\pt > 36 \GeV$
\end{itemize}
For the isolated lepton triggers, the isolation requirement is evaluated 
using the scalar sum of the \pt~of all tracks surrounding the lepton 
(excluding the lepton track itself) in a cone of $\Delta R < 0.2$
such the sum does not exceed 12\% (10\%) of the muon (electron)  \pt.


\subsection{Simulation samples}
%%Do I need to talk about Monte Carlo showering, 
%%hadronization and reconstruction?
%%A general discussion of Monte Carlo could go here

An important tool for the modeling of physics processes
at the LHC is Monte Carlo simulation (MC).
MC relies on random sampling to connect the matrix element formulations
derived from quantum mechanical perturbation theory into 
actual predictions for the results of proton-proton collisions
at the LHC.
The prediction of a single collision from the MC represents
one possible outcome of the proton-proton collision, with all of the 
products of the hard-scattering and their four-momenta.
This result can be passed through additional MC simulation to describe
hadronization and the soft products of the collision e.g. photon radiation.
Finally, these products are passed through a detailed 
simulation of the response of the 
ATLAS detector built in \geant~\cite{Agostinelli:2002hh}
so that the same reconstruction algorithms
can be applied as in the data.
This sampling is repeated many times to populate the 
distribution of possible
outcomes. Dedicated MC programs are provided by theorists for 
different processes to different orders in perturbation theory,
and then interfaced to different PDFs.
Details of the different processes simulated from MC and their
treatment are presented below.




\input{www_signal}
\newpage
\input{www_bg_samples}



